Fourmile

### 2022-07-28 fourmile_dataprocess.Rmd
plotting hydrographs

daily_q <- orun %>%
  select(-1) %>%
  filter(!row_number() %in% c(1:9, 11:15)) %>%
  mutate(names(.) = .[1,])

>>>>

daily_q <- orun %>%
  select(-1) %>%
  filter(!row_number() %in% c(1:9, 11:15)) %>%
  set_names(as.character(slice(., 1))) %>%
  slice(-1) %>%
  replace(.==-9999, NA) %>%
  rename(ds3 = 2,
         usgs1 = 3,
         ds2 = 4,
         usgs2 = 5,
         us1 = 6,
         ds1 = 7) %>%
  mutate(date = mdy(date)) %>%
  pivot_longer(!date, names_to = 'site', values_to = 'q_m3s') %>%
  mutate(q_m3s = as.numeric(q_m3s))

hydro <- ggplot(daily_q, aes(x=date, y=q_m3s, color=site)) + geom_line() +
  ylim(0,8)

ggplotly(hydro)
